---
title: "Case-cohort study design I"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(rje) #for expit
library(survival)
library(survey)
```


## Simulation w/modifications for efficiency
```{r}
bv.simulation <- function(exp.rate, beta, gamma, baseline.hazards,delta, epsilon, zeta) {
# exp.rate is the exposure rate to HIV
# beta is the coefficient (intercept) in generating BV status
# gamma is the coefficient in generate BV status, and varied to control association
# of HIV exposure and BV status
########### main body #############
 # exp.rate=0.3
 # beta=-1.5
 # gamma = 6
 # baseline.hazards = 0.0001405205
 # delta = log(0.5)
 # epsilon = 0
 # zeta =0
# generate sites and participants, sites 1:10, participants per site 1:250
sites <- rep(1:10, each = 250)
participants <- 1:2500
# generate exposure rates for study sites
a.set <- seq(exp.rate-0.16,exp.rate+0.20, 0.04)
# calculate hiv exposure for each site
HIV.exp <- rbinom(2500,1,a.set) # 40%
# generate bv status
bv <- rbinom(2500,1,expit(beta + gamma*HIV.exp)) # 40%, no correlation
# generate the intervention assignment
tx <- rep(c(0,1),times = 125)
# generate the hazards
# overall HIV incidence of 5% per year
individual.hazards <- baseline.hazards*exp(delta*tx+epsilon*bv+zeta*tx*bv)
# set those whose exposure status of 0 to small hazard
individual.hazards.2 <- ifelse(HIV.exp==0, 0.0001, individual.hazards)
Time.to.HIV <- rexp(2500, individual.hazards.2)
# combine and arrange the time to hiv
sort.time <- sort(Time.to.HIV)
# add numbering to the dataset
# set the time to event to NA if  exceed 160 events (study ends when reach 160 events)
censor.time <- ifelse(Time.to.HIV <= sort.time[160], Time.to.HIV, sort.time[160])
# identify those top 160 time to events and label them with HIV infection
HIV.infection <- ifelse(Time.to.HIV <= sort.time[160], 1, 0)
data.frame(sites,participants,HIV.exp,bv,tx,individual.hazards.2,censor.time,HIV.infection)
}
# test the function
set.seed(1)
bv.sim <- bv.simulation(0.3, -1.5, 6, 0.0001405205, log(0.5), 0, 0)
bv.sim %>% filter(HIV.exp == 1)%>% 
  summarise(prop = mean(bv)) %>%
                    .$prop # want this to be close to 1
bv.sim %>% filter(HIV.exp == 0)%>% 
  summarise(prop = mean(bv)) %>%
                    .$prop # want this to be close to 0.2
bv.sim %>% filter(sites == "5") %>%
 summarise(prop = mean(HIV.exp)) %>%
                    .$prop # should be close to 30%
# check the hiv incidence in the control arm
bv.sim %>% filter(tx == 0)%>% 
  summarise(prop = mean(HIV.infection)) %>%
                    .$prop # want this to be close to 0.05
```

```{r}
  # the first set of test is on the placebo group
  placebo <- bv.sim %>% filter(tx == 0)
################## normal cox
  cox.res <- coxph(Surv(Time.to.HIV, HIV.infection) ~ bv, placebo)
  cox.strat <- coxph(Surv(Time.to.HIV, HIV.infection) ~ bv + strata(sites), placebo)
  # strata(sites)
################## srs
  sel.sub <- sample(placebo$participants,125,replace = F)
  placebo$sel.sub <- ifelse(placebo$participants %in% sel.sub, 1, 0)
  selccoh <- with(placebo, HIV.infection==1|sel.sub==1)
  sim.subco <- placebo[selccoh,]
  stratsizes <- table(placebo$sites)
  cch1 <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data = sim.subco, #placebo[filterings]
   subcoh = ~sel.sub, id=~participants, cohort.size=1250, method="Prentice") # stratum = ~ sites
  # stratified
  cch1.strat <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data = sim.subco, #placebo[filterings]
   subcoh = ~sel.sub, id=~participants,stratum = ~sites, cohort.size=stratsizes, method="I.Borgan") # stratum = ~ sites
  
################## covariate adjusted method 1
  incident.per.site <- function(a) {
  placebo %>% filter(sites == a) %>%
  summarise(prop = sum(HIV.infection)) %>%
                    .$prop}
  HIV.probs.list <- as.numeric(lapply(placebo$sites, incident.per.site))/sum(placebo$HIV.infection) # tabulate
  indexes.proportion <- sample(placebo$participants, size = 125, prob = HIV.probs.list[1:1250], replace =   FALSE)
  placebo$site.sel.proportion <- ifelse(placebo$participants %in% indexes.proportion, 1, 0)
  # apply the subcohort analysis
  site.selccoh <- with(placebo, HIV.infection==1|site.sel.proportion==1) ## cases in the subcohort
  # creating the subcohort dataset from the full cohort dataset
  site.sim.subco <- placebo[site.selccoh,]
  site.fit <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data =site.sim.subco,
              subcoh = ~site.sel.proportion, id=~participants, cohort.size=1250, method="Pren")
  site.fit.strat <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data =site.sim.subco,
              subcoh = ~site.sel.proportion, id=~participants,stratum = ~sites ,cohort.size=stratsizes, method="I.Borgan")
  
################# covariate adjusted method 2
  logit1 <- glm(HIV.infection~as.factor(sites), data=placebo, family = "binomial")
  ## use the original method posted in the MORGAM paper to get the probability of getting infection
  placebo$Site.prob <- predict(logit1, newdata = placebo, type = "response")
  indexes.logit <- sample(placebo$participants, size = 125, prob = placebo$Site.prob[1:1250], replace = FALSE)
  # generating the dataset
  placebo$site.sel.logit <- ifelse(placebo$participants %in% indexes.logit, 1, 0)
  # apply the subcohort analysis
  site.selccoh.logit <- with(placebo, HIV.infection==1|site.sel.logit==1) ## cases in the subcohort
  # creating the subcohort dataset from the full cohort dataset
  site.subco.logit <- placebo[site.selccoh.logit,]
  # run subcohort analysis using the cch function with Prentice method
  site.fit.logit <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data =site.subco.logit,
              subcoh = ~site.sel.logit, id=~participants, cohort.size=1250, method="Pren") #Borgan
  site.fit.logit.strat <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data =site.subco.logit,
              subcoh = ~site.sel.logit, id=~participants,stratum = ~sites, cohort.size=stratsizes, method="I.Borgan") #Borgan
  # results
one.result <- matrix(c(cox.res$coefficients, cox.res$var, 
           cox.strat$coefficients,cox.strat$var,
           cch1$coefficients, cch1$var,
           cch1.strat$coefficients,cch1.strat$var,
           site.fit$coefficients, site.fit$var,
           site.fit.strat$coefficients, site.fit.strat$var,
           site.fit.logit$coefficients, site.fit.logit$var,
           site.fit.logit.strat$coefficients, site.fit.logit.strat$var), 
         nrow = 1, byrow = TRUE)
 
one.mean <-  c(one.result[1], one.result[3],one.result[5],one.result[7],one.result[9],one.result[11],one.result[13],               one.result[15])
one.var <- c(one.result[2], one.result[4],one.result[6],one.result[8],one.result[10],one.result[12],one.result[14],
             one.result[16])
one.dat <- data.frame(one.mean,one.var)
rownames(one.dat) <- c("Cox regresion on the placebo arm",
                       "Cox regresion on the placebo arm + stratification",
                          "Case-cohort analysis - SRS",
                       "Stratified Case-cohort analysis - SRS",
                          "Case-cohort analysis - baseline M1",
                       "Stratified Case-cohort analysis - baseline M1",
                          "Case-cohort analysis - baseline M2",
                       "Stratified Case-cohort analysis - baseline M2")
colnames(one.dat) <- c("Sample mean","Sample variance")
one.dat
```
# Function 1: the combined function for testing BV among the placebo group
```{r}
bv.function <- function(a,b,c){ # add a stratification by site
  # the dataset
  bv.sim <- bv.simulation(0.3, -1.5, 6, 0.0001405205, a,b,c)
  # the first set of test is on the placebo group
  placebo <- bv.sim %>% filter(tx == 0)
################## normal cox
  cox.res <- coxph(Surv(Time.to.HIV, HIV.infection) ~ bv, placebo)
  # strata(sites)
################## srs
  sel.sub <- sample(placebo$participants,125,replace = F)
  placebo$sel.sub <- ifelse(placebo$participants %in% sel.sub, 1, 0)
  selccoh <- with(placebo, HIV.infection==1|sel.sub==1)
  sim.subco <- placebo[selccoh,]
  cch1 <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data = sim.subco, #placebo[filterings]
   subcoh = ~sel.sub, id=~participants, cohort.size=1250, method="Prentice") # stratum = ~ sites
  
################## covariate adjusted method 1
  incident.per.site <- function(a) {
  placebo %>% filter(sites == a) %>%
  summarise(prop = sum(HIV.infection)) %>%
                    .$prop}
  HIV.probs.list <- as.numeric(lapply(placebo$sites, incident.per.site))/sum(placebo$HIV.infection) # tabulate
  indexes.proportion <- sample(placebo$participants, size = 125, prob = HIV.probs.list[1:1250], replace =   FALSE)
  placebo$site.sel.proportion <- ifelse(placebo$participants %in% indexes.proportion, 1, 0)
  # apply the subcohort analysis
  site.selccoh <- with(placebo, HIV.infection==1|site.sel.proportion==1) ## cases in the subcohort
  # creating the subcohort dataset from the full cohort dataset
  site.sim.subco <- placebo[site.selccoh,]
  site.fit <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data =site.sim.subco,
              subcoh = ~site.sel.proportion, id=~participants, cohort.size=1250, method="Pren")
  
################# covariate adjusted method 2
  logit1 <- glm(HIV.infection~as.factor(sites), data=placebo, family = "binomial")
  ## use the original method posted in the MORGAM paper to get the probability of getting infection
  placebo$Site.prob <- predict(logit1, newdata = placebo, type = "response")
  indexes.logit <- sample(placebo$participants, size = 125, prob = placebo$Site.prob[1:1250], replace = FALSE)
  # generating the dataset
  placebo$site.sel.logit <- ifelse(placebo$participants %in% indexes.logit, 1, 0)
  # apply the subcohort analysis
  site.selccoh.logit <- with(placebo, HIV.infection==1|site.sel.logit==1) ## cases in the subcohort
  # creating the subcohort dataset from the full cohort dataset
  site.subco.logit <- placebo[site.selccoh.logit,]
  # run subcohort analysis using the cch function with Prentice method
  site.fit.logit <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv, data =site.subco.logit,
              subcoh = ~site.sel.logit, id=~participants, cohort.size=1250, method="Pren") #Borgan
  # results
  matrix(c(cox.res$coefficients, cox.res$var, cch1$coefficients, cch1$var,
           site.fit$coefficients, site.fit$var, site.fit.logit$coefficients, site.fit.logit$var), 
         nrow = 1, byrow = TRUE)
}

bv.function(log(0.5), 0, 0)

mat.1 <- replicate(1000, bv.function(log(0.5), 0, 0))
first.set <- matrix(mat.1, nrow = 1000, byrow = TRUE)
result1.mean <- apply(first.set, 2, mean)
result1.sd <- apply(first.set, 2, sd)
mean1 <- c(result1.mean[1], result1.mean[3],result1.mean[5],result1.mean[7])
var1 <- c(result1.mean[2], result1.mean[4],result1.mean[6],result1.mean[8])
sd.mean1 <- c(result1.sd[1], result1.sd[3],result1.sd[5],result1.sd[7])
sd.var1 <- c(result1.sd[2], result1.sd[4],result1.sd[6],result1.sd[8])
result1 <- data.frame(mean1,var1,sd.mean1,sd.var1)
rownames(result1) <- c("Cox regresion on the placebo arm",
                          "Case-cohort analysis - SRS",
                          "Case-cohort analysis - baseline M1",
                          "Case-cohort analysis - baseline M2")
colnames(result1) <- c("Average sample mean","Average sample variance","Sample standard deviation","Sample SD of variance")
result1
```
# Function 2: the combined function to test the interaction term
```{r}
bv.EF.function <- function(a,b,c){
  # the dataset
  bv.sim <- bv.simulation(0.3, -1.5, 6, 0.0001405205, a,b,c)
################## normal cox
  cox.res <- coxph(Surv(Time.to.HIV, HIV.infection) ~ bv*tx, bv.sim)
  
################## srs
  sel.sub <- sample(bv.sim$participants,250,replace = F)
  bv.sim$sel.sub <- ifelse(bv.sim$participants %in% sel.sub, 1, 0)
  selccoh <- with(bv.sim, HIV.infection==1|sel.sub==1)
  sim.subco <- bv.sim[selccoh,]
  cch1 <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv*tx, data =sim.subco,
   subcoh = ~sel.sub, id=~participants, cohort.size=2500, method="Prentice")
  
################## covariate adjusted method 1
  incident.per.site <- function(a) {
  bv.sim %>% filter(sites == a) %>%
  summarise(prop = sum(HIV.infection)) %>%
                    .$prop}
  HIV.probs.list <- as.numeric(lapply( bv.sim$sites, incident.per.site))/sum( bv.sim$HIV.infection)
  indexes.proportion <- sample( bv.sim$participants, size = 250, prob = HIV.probs.list[1:2500], replace =   FALSE)
   bv.sim$site.sel.proportion <- ifelse( bv.sim$participants %in% indexes.proportion, 1, 0)
  # apply the subcohort analysis
  site.selccoh <- with( bv.sim, HIV.infection==1|site.sel.proportion==1) ## cases in the subcohort
  # creating the subcohort dataset from the full cohort dataset
  site.sim.subco <-  bv.sim[site.selccoh,]
  site.fit <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv*tx, data =site.sim.subco,
              subcoh = ~site.sel.proportion, id=~participants, cohort.size=2500, method="Pren")
  
################# covariate adjusted method 2
  logit1 <- glm(HIV.infection~as.factor(sites), data= bv.sim, family = "binomial")
  ## use the original method posted in the MORGAM paper to get the probability of getting infection
  bv.sim$Site.prob <- predict(logit1, newdata =  bv.sim, type = "response")
  indexes.logit <- sample( bv.sim$participants, size = 250, prob =  bv.sim$Site.prob[1:2500], replace = FALSE)
  # generating the dataset
   bv.sim$site.sel.logit <- ifelse( bv.sim$participants %in% indexes.logit, 1, 0)
  # apply the subcohort analysis
  site.selccoh.logit <- with( bv.sim, HIV.infection==1|site.sel.logit==1) ## cases in the subcohort
  # creating the subcohort dataset from the full cohort dataset
  site.subco.logit <-  bv.sim[site.selccoh.logit,]
  # run subcohort analysis using the cch function with Prentice method
  site.fit.logit <- cch(Surv(Time.to.HIV, HIV.infection) ~ bv*tx, data =site.subco.logit,
              subcoh = ~site.sel.logit, id=~participants, cohort.size=2500, method="Pren")
  # results
matrix(c(cox.res$coefficients[1], cox.res$coefficients[2],cox.res$coefficients[3],
         cox.res$var[1],cox.res$var[2],cox.res$var[3],
         cch1$coefficients[1], cch1$coefficients[2],cch1$coefficients[3],
         cch1$var[1],cch1$var[2],cch1$var[3],
         site.fit$coefficients[1], site.fit$coefficients[2],site.fit$coefficients[3],
         site.fit$var[1],site.fit$var[2],site.fit$var[3],
         site.fit.logit$coefficients[1], site.fit.logit$coefficients[2],site.fit.logit$coefficients[3],
         site.fit.logit$var[1],site.fit.logit$var[2],site.fit.logit$var[3]), nrow = 1, byrow = TRUE)
}
bv.EF.function(log(0.5), 0, 0)

mat.2 <- replicate(1000, bv.EF.function(log(0.5), 0, 0)) # save this into a R data
save(mat.2,file = "Result2.RData")
second.set <- matrix(mat.2, nrow = 1000, byrow = TRUE)
save(second.set,file = "Result2.RData")
result2.mean <- apply(second.set, 2, mean)
result2.sd <- apply(second.set, 2, sd)
mean2.beta1 <- c(result2.mean[1], result2.mean[7],result2.mean[13],result2.mean[19])
mean2.beta2 <- c(result2.mean[2], result2.mean[8],result2.mean[14],result2.mean[20])
mean2.beta3 <- c(result2.mean[3], result2.mean[9],result2.mean[15],result2.mean[21])
var2.beta1 <-  c(result2.mean[4], result2.mean[10],result2.mean[16],result2.mean[22])
var2.beta2 <-  c(result2.mean[5], result2.mean[11],result2.mean[17],result2.mean[23])
var2.beta3 <-  c(result2.mean[6], result2.mean[12],result2.mean[18],result2.mean[24])
sd.mean.beta1 <- c(result2.sd[1], result2.sd[7],result2.sd[13],result2.sd[19])
sd.mean.beta2 <- c(result2.sd[2], result2.sd[8],result2.sd[14],result2.sd[20])
sd.mean.beta3 <- c(result2.sd[3], result2.sd[9],result2.sd[15],result2.sd[21])
sd.var.beta1 <- c(result2.sd[4], result2.sd[10],result2.sd[16],result2.sd[22])
sd.var.beta2 <- c(result2.sd[5], result2.sd[11],result2.sd[17],result2.sd[23])
sd.var.beta3 <- c(result2.sd[6], result2.sd[12],result2.sd[18],result2.sd[24])
result2 <- data.frame(mean2.beta1,mean2.beta2,mean2.beta3,var2.beta1,var2.beta2,var2.beta3,
              sd.mean.beta1,sd.mean.beta2,sd.mean.beta3,
              sd.var.beta1,sd.var.beta2,sd.var.beta3)
rownames(result2) <- c("Cox regresion on everyone",
                          "Case-cohort analysis - SRS",
                          "Case-cohort analysis - baseline M1",
                          "Case-cohort analysis - baseline M2")
colnames(result2) <- c("B1 average sample mean", "B2 average sample mean","B3 average sample mean",
                       "B1 average variance","B2 average variance","B3 average variance",
                       "B1 SD of sample mean","B2 SD of sample mean","B3 SD of sample mean",
                       "B1 SD of variance","B2 SD of variance","B3 SD of variance")
result2
mat.2
```

# The two-phase sampling method in Survey package
# the simulation function
Get the exposure and bv not correlated to see the outcomes.
```{r simulation}
bv.simulation.2 <- function(exp.rate, beta, gamma, baseline.hazards, epsilon) {
# exp.rate is the exposure rate to HIV
# beta is the coefficient (intercept) in generating BV status
# gamma is the coefficient in generate BV status, and varied to control association
# of HIV exposure and BV status
  ########### main body #############
# generate sites and participants, sites 1:10, participants per site 1:250
sites <- rep(1:10, each = 250)
participants <- 1:2500
# generate exposure rates for study sites
# a.set <- seq(exp.rate-0.16,exp.rate+0.20, 0.04)
# calculate hiv exposure for each site
HIV.exp <- rbinom(2500,1,exp.rate) # varying by site as the original simulation plan
# generate bv status
bv <- rbinom(2500,1,expit(beta + gamma*HIV.exp))# correlation with HIV exp varies, increase gamma and cut beta
# generate the intervention assignment
# tx <- rep(c(0,1),times = 125)
# generate the hazards
# overall HIV incidence of 5% per year
individual.hazards <- baseline.hazards*exp(epsilon*bv) # only epsilon
# set those whose exposure status of 0 to small hazard
individual.hazards.2 <- ifelse(HIV.exp==0, 0.00001, individual.hazards)
Time.to.HIV <- rexp(2500, individual.hazards.2)
# combine and arrange the time to hiv
sort.time <- sort(Time.to.HIV)
sort.time[160]
# add numbering to the dataset
# set the time to event to NA if  exceed 160 events (study ends when reach 160 events)
Time.to.HIV <- ifelse(Time.to.HIV <= sort.time[160], Time.to.HIV, sort.time[160]+1)
# identify those top 160 time to events and label them with HIV infection
HIV.infection <- ifelse(Time.to.HIV <= sort.time[160], 1, 0)
data.frame(sites,participants,HIV.exp,bv,individual.hazards.2,Time.to.HIV,HIV.infection)
} # wait until the end to combine the data
# test the function
bv.sim.2 <- bv.simulation.2(0.4, -1.5, 2.5, 0.0001405205, 0)

bv.sim.2 %>% summarise(prop = mean(bv)) %>%
                    .$prop  # should be close to 40%
bv.sim.2 %>% summarise(prop = mean(HIV.exp)) %>%
                    .$prop # should be close to 40%
```

# Implementing the survey package: Lin & Ying
```{r}
# simple random
rep.svy.LY <- function(hiv.exp, beta, gamma) {
bv.sim.2 <- bv.simulation.2(hiv.exp, beta, gamma, 0.0001405205, 0)

sel.sub <- sample(bv.sim.2$participants,250,replace = F)
bv.sim.2$sel.sub <- ifelse(bv.sim.2$participants %in% sel.sub, 1, 0)

dcch<-twophase(id=list(~participants,~participants), strata=list(NULL,~HIV.infection),
                  subset=~I(sel.sub | HIV.infection), data=bv.sim.2)
fit1 <- svycoxph(Surv(Time.to.HIV,HIV.infection)~bv+strata(sites),
                design=dcch)
# probabilities
rates <- rep(0,10)
  for (i in 1:10) {
  rates[i] <- bv.sim.2 %>% filter(sites == i) %>%
  summarise(prop = mean(HIV.infection)) %>%
                    .$prop
  }
  HIV.probs.list <- rep(rates, each = 250)# tabulate
  indexes.proportion <- sample(bv.sim.2$participants, size = 250, prob = HIV.probs.list, replace =   FALSE)
  bv.sim.2$site.sel.proportion <- ifelse(bv.sim.2$participants %in% indexes.proportion, 1, 0)

dcch.site1<-twophase(id=list(~participants,~participants), strata=list(NULL,~HIV.infection),
                  subset=~I(site.sel.proportion | HIV.infection), data=bv.sim.2)
fit2 <- svycoxph(Surv(Time.to.HIV,HIV.infection)~bv+strata(sites),
                design=dcch.site1)
# logistic
  logit1 <- glm(HIV.infection~as.factor(sites), data=bv.sim.2, family = "binomial")
  ## use the original method posted in the MORGAM paper to get the probability of getting infection
  bv.sim.2$Site.prob <- predict(logit1, newdata = bv.sim.2, type = "response")
  indexes.logit <- sample(bv.sim.2$participants, size = 250, prob = bv.sim.2$Site.prob[1:2500], replace = FALSE)
  # generating the dataset
  bv.sim.2$site.sel.logit <- ifelse(bv.sim.2$participants %in% indexes.logit, 1, 0)
dcch.site2<-twophase(id=list(~participants,~participants), strata=list(NULL,~HIV.infection),
                  subset=~I(site.sel.logit | HIV.infection), data=bv.sim.2)
fit3 <- svycoxph(Surv(Time.to.HIV,HIV.infection)~bv+strata(sites),
                design=dcch.site2)
matrix(c(fit1$coefficients,fit1$var,
         fit2$coefficients,fit2$var,
         fit3$coefficients,fit3$var), byrow = TRUE)
}
mat1 <- replicate(1000,rep.svy.LY(0.4, -1.5, 2.5))

convert_to_table <- function(dataset,n) {
first.set <- matrix(dataset, nrow = n, byrow = TRUE)
result1.mean <- apply(first.set, 2, mean)
table1 <- matrix(result1.mean, nrow = 3, byrow = TRUE)
colnames(table1) <- c("mean","variance")
rownames(table1) <- c("SRS","Baseline-adjusted 1","Baseline-adjusted 2")
table1
}

```
# Implementing the stratified design (Borgan)
```{r}

rep.svy.Borgan <- function(hiv.exp, beta, gamma) {
bv.sim.2 <- bv.simulation.2(hiv.exp, beta, gamma, 0.0001405205, 0)

sel.sub <- sample(bv.sim.2$participants,250,replace = F)
bv.sim.2$sel.sub <- ifelse(bv.sim.2$participants %in% sel.sub, 1, 0)

d_BorganII <- twophase(id=list(~participants,~participants), strata=list(NULL,~interaction(sites,HIV.infection)),
                  subset=~I(sel.sub | HIV.infection), data=bv.sim.2)
b1 <-svycoxph(Surv(Time.to.HIV,HIV.infection)~bv+strata(sites),
                design=d_BorganII)
# probabilities
rates <- rep(0,10)
  for (i in 1:10) {
  rates[i] <- bv.sim.2 %>% filter(sites == i) %>%
  summarise(prop = mean(HIV.infection)) %>%
                    .$prop
  }
  HIV.probs.list <- rep(rates, each = 250)# tabulate
  indexes.proportion <- sample(bv.sim.2$participants, size = 250, prob = HIV.probs.list, replace =   FALSE)
  bv.sim.2$site.sel.proportion <- ifelse(bv.sim.2$participants %in% indexes.proportion, 1, 0)

borgan.site1<-twophase(id=list(~participants,~participants), strata=list(NULL,~interaction(sites,HIV.infection)),
                  subset=~I(site.sel.proportion | HIV.infection), data=bv.sim.2)
b2 <- svycoxph(Surv(Time.to.HIV,HIV.infection)~bv+strata(sites),
                design=borgan.site1)

# logistic
  logit1 <- glm(HIV.infection~as.factor(sites), data=bv.sim.2, family = "binomial")
  ## use the original method posted in the MORGAM paper to get the probability of getting infection
  bv.sim.2$Site.prob <- predict(logit1, newdata = bv.sim.2, type = "response")
  indexes.logit <- sample(bv.sim.2$participants, size = 250, prob = bv.sim.2$Site.prob[1:2500], replace = FALSE)
  # generating the dataset
  bv.sim.2$site.sel.logit <- ifelse(bv.sim.2$participants %in% indexes.logit, 1, 0)

borgan.site2<-twophase(id=list(~participants,~participants), strata=list(NULL,~interaction(sites,HIV.infection)),
                  subset=~I(site.sel.logit | HIV.infection), data=bv.sim.2)
b3 <- svycoxph(Surv(Time.to.HIV,HIV.infection)~bv+strata(sites),
                design=borgan.site2)
matrix(c(b1$coefficients,b1$var,
         b2$coefficients,b2$var,
         b3$coefficients,b3$var), byrow = TRUE)
}

mat2 <- replicate(1000,rep.svy.Borgan(0.4, -1.5, 2.5))
second.set <- matrix(mat2, nrow = 1000, byrow = TRUE)
result2.mean <- apply(second.set, 2, mean)


```

# Result summary
```{r}
exp.rate <- 0.2
beta <- 0
gamma <- 6.0
HIV.exp <- rbinom(2500,1,exp.rate)
bv <- rbinom(2500,1,expit(beta + gamma*HIV.exp))
mean(bv)

# 40% HIV, 40% BV, beta = -1.5, gamma = 2.5
(LY.40.40 <- convert_to_table(mat1, 1000))
(B.40.40 <- convert_to_table(mat2, 1000))
# 20% HIV, 20% BV, beta = -1.9, gamma = 2.0
mat1.20.20 <- replicate(1000,rep.svy.LY(0.2, -1.9, 2.0))
mat2.20.20 <- replicate(1000,rep.svy.Borgan(0.2, -1.9, 2.0))
(LY.20.20 <- convert_to_table(mat1.20.20, 1000))
(B.20.20 <- convert_to_table(mat2.20.20, 1000))
# 60% HIV, 60% BV, beta = -1.5, gamma = 3.5
mat1.60.60 <- replicate(1000,rep.svy.LY(0.6, -1.5, 3.5))
mat2.60.60 <- replicate(1000,rep.svy.Borgan(0.6, -1.5, 3.5))
(LY.60.60 <- convert_to_table(mat1.60.60, 1000))
(B.60.60 <- convert_to_table(mat2.60.60, 1000))
# 60% HIV, 20% BV, beta = -1.7, gamma = 0.5
mat1.60.20 <- replicate(1000,rep.svy.LY(0.6, -1.7, 0.5))
mat2.60.20 <- replicate(1000,rep.svy.Borgan(0.6, -1.7, 0.5))
(LY.60.20 <- convert_to_table(mat1.60.20, 1000))
(B.60.20 <- convert_to_table(mat2.60.20, 1000))
# 20% HIV, 60% BV, beta = 0, gamma = 6.0
mat1.20.60 <- replicate(1000,rep.svy.LY(0.2, 0, 6.0))
mat2.20.60 <- replicate(1000,rep.svy.Borgan(0.2, 0, 6.0))
(LY.20.60 <- convert_to_table(mat1.20.60, 1000))
(B.20.60 <- convert_to_table(mat2.20.60, 1000))

```